\documentclass[10pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{CJK}					% 支持中文
\usepackage{indentfirst}			% 首行缩进宏包
\usepackage{fancyhdr}			% 添加页眉
\setlength{\parindent}{2em}		% 缩进距离为2个字符位置
\newcommand{\song}{\CJKfamily{song}}		% 宋体
\newcommand{\hei}{\CJKfamily{hei}}      	% 黑体
\newcommand{\fs}{\CJKfamily{fang}}       % 仿宋
\newcommand{\kai}{\CJKfamily{kai}}       % 楷体
\newcommand{\li}{\CJKfamily{li}}         % 隶书
\newcommand{\you}{\CJKfamily{you}}       % 幼圆


\begin{document}
\begin{CJK*}{UTF8}{gkai}
\pagestyle{fancy} 
\lhead{}
\chead{\small{Homework of Postgraduate English}}
\rhead{}
%============================++题目和作者++================================
\title{Personal Statement}					   		% 题目
\author{郝俊禹\thanks{Email:haojunyu2012@gmail.com}}	% 作者
\maketitle 											% 生成标题
\thispagestyle{fancy}    							% 设置本页风格                            %============================++++正文++++=================================
My name is Hao Junyu.My hometown is yangzhou city in jiangsu province. Last year I finished my undergraduate education in SuZhou University, Majoring in Computer Science and Technology in the college of Computer Science and Technology. Now I am studying in Tong-Ji University for another two and a half years.


I am open-minded, willing and have broad interests like basketball, reading and especially in engineering such as software programming, website design. For example, during the past two years, I have accomplished a website--tracking system. This system is to help help mentors manage the daily work and research of graduates. To my happiness, the website is running in       SuZhou University.


Although I have broad interests in many aspects and grasp the essential knowledge of the major, but I think at present, I can do many things in a superficial level, but not be competent to do things professionally owing to lack of ample knowledge and ability. So I think further study is still urgent for me to realize self-value.


I plan to concentrate on study and research in this field in my graduate time. And I hope I can form a systematic view of computer technology and make a solid foundation for future profession after two and a half years study here.













%============================+++++++++++=================================
\clearpage     
\end{CJK*}
\end{document}