\documentclass[12pt,a4paper]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{CJK}					% 支持中文
\usepackage{indentfirst}			% 首行缩进宏包
\usepackage{fancyhdr}			% 添加页眉
\usepackage{tipa}

\setlength{\parindent}{2em}		% 缩进距离为2个字符位置

\begin{document}\large
\pagestyle{fancy} 
\lhead{}
\chead{\small{Homework of Postgraduate English}}
\rhead{}
%============================++题目和作者++================================
\title{Enlightenment from Nokia's Rise and Decline}	   		% 题目
\author{haojunyu\thanks{Email:haojunyu2012@gmail.com}}	% 作者
\maketitle 											% 生成标题
\thispagestyle{fancy}    							% 设置本页风格                            
%============================++++正文++++=================================
Here are two mobile phones from Nokia, One is Nokia 3100,which is produced
in 2003. and the other one is N97 produced in 2009. From the sales of these
two, we can see the glory of Nokia.\\


In Sep 3, 2013, A surprising news hits the IT industry, Microsoft acquired Nokia's handset business for \${}7.2 billion. This indicates the beginning of Nokia's fall.\\


From the Rise and fall in Nokia, we can get three enlightenments.

 Firstly, competition is cruel, except for market. Nokia, a huge company, fall down in such a  quick speed. Samsung and Apple all give a hand to this. 
 
 
Secondly, Nokia can not grasp the direction of market. When Google develops the android system, Nokia devotes 
itself to Symbain system. 


Last but not least, Nokia is always lost themselves in the past glory, so that it misses the opportunity to rise again.

 


























%============================+++++++++++=================================
\clearpage     
\end{document}