\documentclass[11pt,a4paper,nolmodern]{moderncv}
\usepackage[noindent,UTF8]{ctex}
\usepackage{info}

\title{College of Electronics and Information Engineering}
%\myquote{自强不息，厚德载物。}{}

\begin{document}
\setmainfont{Adobe Fangsong Std}
\setsansfont{Adobe Kaiti Std}

\hyphenpenalty=10000
\maketitle

%\section{Job Intension}
%\cvhobby{job objective}{Data Mining, Machine Learning}
%\cvhobby{Cause}{During the Undergraduate stage, I participated in some competitions and developed some management system. However, as the time of Big Data is coming, I want to do some research on Data Mining and Machine Learning at the graduate level. So I not only study the course--Machine Learning teaching by Andrew\,Ng on my own, but also complete a paper on deep\,learning and bayesian network under the guidance of my supervisor. I wish to get this position and apply what I have learned in practice.}

\section{Education}
\tlcventry{2013}{0}{Master, College of Electronics and Information Engineering, Tongji University}{}{}{}{
\begin{itemize}
  \item 2014, complete the thesis <DISCRIMINATION OF ADHD CHILDREN BASED ON DEEP BAYESIAN NETWORK> 
\end{itemize}}
\tlcventry{2009}{2013}{Bachelor, College of Computer Science and Technology, Soochow University}{}{}{}{
\begin{itemize}
  %\item 2010年，获苏州大学学习优秀奖学金
  \item 2011, The Second Prize of National Undergraduate Mathematical Contest in Modeling
  %\item 2011年，获“国信蓝点杯”全国软件专业人才设计与开发大赛江苏赛区C语言程序设计本科组二等奖
  %\item 2011年，获苏州大学人民综合一等奖学金、苏州大学三好学生、国家励志奖学金
  %\item 2012年，获美国大学生数学建模竞赛二等奖
  \item 2012, The Third Prize in The Design and Development of National Software Contest for
Java language
\end{itemize}}
\section{Professional Skill}
\subsection{Development}
\cvcomputer{language}{C/C++(Familiar), C\#, Java}
           {Web}{HTML, ASP .Net}  
\cvcomputer{Database}{MySQL(Familiar), SQL Server}
			{Tools}{Matlab, Shell,Python}

\subsection{others}
\cvcomputer{Blog}{ Github }
           {Editor}{\LaTeX{}，VIM}

\section{Experience}
\subsection{Project Experience}
\tlcventry{2010}{2011}{Management system}{}{}{}{
\begin{itemize}
 \item It’s used to manage the graduate students’ daily study.
 \item Develop B/S mode application Using the technology of Web Service and the SOA frame.
 \item This project help me be familiar with SQL.
\end{itemize}}
\vspace{0.5em}

\tlcventry{2012}{2013}{Scheduling server software}{}{}{}{
\begin{itemize}
 \item Virtual Desktop System includes scheduling server, application server and client, providing support for cloud computing.
 \item Develop the scheduling server software in the virtual desktop system using the technology of socket communication and multithread programming.
 \item This software is only used for laboratory test
\end{itemize}}
\vspace{0.5em}

\tlcventry{2014}{0}{Android Application Development based on ENLU}{}{}{}{
\begin{itemize}
 \item The Android Application aims at helping users to manage the applications by voice
 \item It can analysis user's intention by voice and do the corresponding operation.
 \item This makes me know more about Natural Language Understanding.
\end{itemize}}

\tlcventry{2014}{2015}{Web Application Development based on Django}{}{}{}{
\begin{itemize}
 \item The Web Application based on Django framework aims at constructing training management platform of Nuance company. 
 \item It accepts the training datasets uploaded and trains in server.  
 \item This makes me familiar with python, mysql and html.
\end{itemize}}

\tlcventry{2014}{2015}{DISCRIMINATION OF ADHD CHILDREN BASED ON DEEP BAYESIAN NETWORK}{}{}{}{
\begin{itemize}
 \item The project applies Deep Bayesian Network to discriminate the ADHD children based on FMRI data. 
 \item It refers to Deep Belief Network, Bayesian Network and SVM.  
 \item This makes me apply methods of machine learning into the study of medicine.
\end{itemize}}

\subsection{School Experience}
\tlcventry{2013}{2014}{Minister, Academic Department, College of Computer Science and Technology}{}{}{}{
\begin{itemize}
 \item Responsible for planning and organizing academic lectures, academic salon and so on
 \item Participate in the planning and organization of ”Tongji Girl Day Activity”
\end{itemize}}
\tlcventry{2014}{2015}{Develop department of Nuance Company}{}{}{}{
\begin{itemize}
 \item Apply the ENLU libary into the application in android phone.
 \item Develop the Task Management System based on Django.
\end{itemize}}
\tlcventry{2015}{0}{Develop and Operation department of SAP company}{}{}{}{
\begin{itemize}
 \item Build up the ELK system.
 \item Analysis the user behaviour and system status.
\end{itemize}}


\section{Interests}

\cvhobby{sports}{table tennis, swimming}
\cvhobby{others}{Travel, reading, photography}

\end{document}

